An Algorithm for In-Situ Bus Scheduling and Passenger State Update

### 2019-04-22 Report/paper.tex
Revised and extended the results and evaluation section

% Sections
\section{Assignment Description}
Your final project report should include:
\begin{itemize}
	\item A write-up describing
	\begin{itemize}
		\item The design rationale of the module(s) you developed, along with the algorithm you have designed/used and a detailed API
		\item Instructions and illustration of use, in terms of a README file and/or user guide,
		\item How your implementation has been tested,
		\item Performance of your implementation,
		\item Assumptions or limitations of your design,
		\item Any omissions or errors in your implementation, and
		\item Any bugs or weaknesses you have found in the algorithm/protocol. (Only if some of these do not apply to your project should you omit them.)
	\end{itemize}
	\item Program sources and executable (including any test programs). Credit will be reserved for the quality of documentation of your programs.
	\item Script of a session showing the program under test.
\end{itemize}

@@

\subsubsection{Request Patterns}
A variety of request patterns were used for evaluation. The scale of these patterns range from two passengers to ???, from two bus stops to ???, and from two buses to ???.

@@

Since a bus will never change its route, it is trivial to predict exactly where it will be along its route at a given point in time. This information can then be used to determine, at the time a request is made, when the next bus to that stop will arrive and how long it will take to arrive at the request's destination. If any request cannot be served in time, an extra bus must be placed in the network. By repeatedly applying these calculations, we compute the minimum number of buses required to serve all requests in time.

\setlength{\tabcolsep}{1em}
\begin{table}[htbp]
\centering
\caption{Evaluating the Traversal Approach.}
\begin{tabular}{c c c}
Request Pattern & Min \# of Buses & Total Lateness \\ \hline
1P\_2S\_1B & $1$ & $-8$ \\
2P\_2S\_1B & $1$ & $-1$ \\
2P\_4S\_1B & $2$ & $5$ \\
\hline
\end{tabular}
\label{tbl:traversal}
\end{table}

Care was taken when devising the Request Patterns not to intentionally disadvantage the static approach. Considerations made include accounting for the fact that, in the real world, passengers will be aware of the schedule and will appear at stops approximately when a bus would be there. However, the results to point to the fact that the Smart Bus algorithm improves on the traversal approach for these patterns.

\section{Using the Smart-Bus Application}
There are several steps to running the application:
\begin{itemize}
	\item Launch $n$ instances of \lstinline{Bus-Driver}
	\item Launch $m$ instances of \lstinline{Bus-Stop-Driver}
	\item Ensure the simulation parameters of \lstinline{Request-Driver} match the number of buses and stops that have been launched
	\item Launch an instance of \lstinline{Request-Driver} with the requisite simulation parameters (i.e., Request Pattern and Time Multiplier)
	\item Wait for simulation to conclude
\end{itemize}

@@

\newpage
\appendix
\section{Source Code}

>>>>

% Sections
% \section{Assignment Description}
% Your final project report should include:
% \begin{itemize}
% 	\item A write-up describing
% 	\begin{itemize}
% 		\item The design rationale of the module(s) you developed, along with the algorithm you have designed/used and a detailed API
% 		\item Instructions and illustration of use, in terms of a README file and/or user guide,
% 		\item How your implementation has been tested,
% 		\item Performance of your implementation,
% 		\item Assumptions or limitations of your design,
% 		\item Any omissions or errors in your implementation, and
% 		\item Any bugs or weaknesses you have found in the algorithm/protocol. (Only if some of these do not apply to your project should you omit them.)
% 	\end{itemize}
% 	\item Program sources and executable (including any test programs). Credit will be reserved for the quality of documentation of your programs.
% 	\item Script of a session showing the program under test.
% \end{itemize}

@@

\subsubsection{Request Patterns}
A variety of request patterns were used for evaluation. The scale of these patterns range from two passengers to eight, from two bus stops to eight, and from one bus to four. The naming scheme depicts the number of passengers (\lstinline{P}), the number of bus stops (\lstinline{S}), and the number of buses it expects (\lstinline{B}). For example, a request pattern wihch produces requests for 6 passengers, in a network with 4 bus stops and 3 buses would have the name 6P\_4S\_3B.

Table~\ref{tbl:smart-bus} summarizes the results for those Request Patterns in which the Emulator network bug did not manifest, or if it did, those patterns for which we could manually compute the lateness and minimum number of buses required.\footnote{Minimum No. of Buses is the smallest number of buses for which the lateness $\ell \leq 0$, or the number of buses which gives the lowest total lateness if it it not possible to serve all requests on time.}

\setlength{\tabcolsep}{1em}
\begin{table}[htbp]
\centering
\caption{Evaluating the Smart Bus Approach.}
\begin{tabular}{c c c}
Request Pattern & Total Lateness & Minimum No. of Buses \\ \hline
1P\_2S\_1B & $-3$ & $1$ \\
2P\_2S\_1B & $-7$ & $1$ \\
2P\_4S\_1B & $2$  & $2$ \\
\end{tabular}
\label{tbl:smart-bus}
\end{table}

@@

Since a bus will never change its route, it is trivial to predict exactly where it will be along its route at a given point in time. This information can then be used to determine, at the time a request is made, when the next bus to that stop will arrive and how long it will take to arrive at the request's destination. If any request cannot be served in time, an extra bus must be placed in the network. By repeatedly applying these calculations, we compute the minimum number of buses required to serve all requests in time. The results are summarized in Table~\ref{tbl:traversal}.

\setlength{\tabcolsep}{1em}
\begin{table}[htbp]
\centering
\caption{Evaluating the Traversal Approach.}
\begin{tabular}{c c c}
Request Pattern & Total Lateness & Minimum No. of Buses \\ \hline
1P\_2S\_1B & $-6$ & $1$ \\
2P\_2S\_1B & $-1$ & $1$ \\
2P\_4S\_1B & $5$  & $2$ \\
\end{tabular}
\label{tbl:traversal}
\end{table}

Care was taken when devising the Request Patterns not to intentionally disadvantage the static approach. Considerations made include accounting for the fact that, in the real world, passengers will be aware of the schedule and will appear at stops approximately when a bus would be there. However, the results point to the fact that the Smart Bus algorithm improves on the traversal approach for these patterns.

\section{Using the Smart-Bus Application}
There are several steps to running the application, which must be done in order:
\begin{itemize}
  \item Launch a \emph{fresh} instance of the Samraksh Emulator NetworkHub
	\item Launch $n$ instances of \lstinline{Bus-Stop-Driver}
	\item Launch $m$ instances of \lstinline{Bus-Driver}
	\item Ensure the simulation parameters of \lstinline{Request-Driver} match the number of buses and stops that have been launched
	\item Launch a single instance of \lstinline{Request-Driver} with the requisite simulation parameters (i.e., Request Pattern and Time Multiplier)
	\item Wait for simulation to conclude
\end{itemize}

The order of these steps is imperative because the Request Driver relies on predictable Bus Stop IDs, which are assigned based on the \lstinline{appId} given to the node from the network. Specifically, the Request Driver expects that Bus Stop nodes have consecutive IDs in $[1, n]$.

@@
